An empirical study of fixation for strategies in the Iterated Prisoner's Dilemma

### 2017-04-27 tex/main.tex
More analysis and writing:
- Add discussion about numerical inversion;
- Add plots of relative fitness for validation strategy pairs
- Particular section for N=2

Various other changes.

The analytical models of a Moran process are based on the relative fitness
between two strategies and take this to be a fixed value \(r\) \cite{Nowak}.
This is a valid model for simple strategies of the Prisoner's Dilemma such as to
\textit{always cooperate} or \textit{always defect}. This manuscript provides a
detailed numerical analysis of \textbf{172} complex and adaptive strategies for
the IPD\@. In this case the relative fitness of a strategy is dependent on the
population distribution.

@@

The contribution of this work is a detailed and extensive analysis of absorption
probabilities for 172 strategies. These strategies and the numerical simulations
are from~\cite{axelrodproject} which is an open source research library written
for the study of the IPD\@. The strategies and simulation frameworks are
automatically tested in accordance to best research software practice. The large
number of strategies are available thanks to the open source nature of the
project with over 40 contributions made by different programmers. Thus by
considering Moran processes with population size greater than 2 we are taking in
to account the effect of complex population dynamics. By considering
sophisticated strategies we are taking in to effect the reputation of a strategy
during each interaction.

@@

To carry out this large numerical experiment 172 strategies are used from
\cite{axelrodproject}. These include 169 default strategies in the library at
the time (excluding strategies classified as having a long run time) as well as
the following 3 finite state machine machine strategies \cite{Ashlock2006}:

@@

Figure~\ref{fig:number_of_stochastic_match_outcomes} shows the distribution of
the number of outcomes between all strategy pairs.
Tables~\ref{tbl:number_of_stochastic_match_outcomes} shows that 95\% of the
stochastic matches have less than 786 unique outcomes whilst the maximum number
is 971. This ensures that using a set of cached results from 1000 precomputed
matches is sufficient for the analysis taking place here.

@@

Figure~\ref{fig:comparison_stochastic} shows the fixation probabilities for
stochastic strategies. These are no longer a good match which highlights the
weakness of the analytical formulae that relies on the average payoffs. A
detailed analysis of the 172 strategies considered, using direct Moran processes
will be shown in the next Section.

@@

\begin{itemize}
    \item Section~\ref{sec:two_individuals} will consider the specific case of
        \(N=2\).
    \item Section~\ref{sec:strong_invaders} will investigate the effect of
        population size on the ability of a strategy to invade another
        population. This will highlight how complex strategies with long
        memories outperform simpler strategies.
    \item Section~\ref{sec:strong_resistors} will similarly investigate the
        ability to defend against an invasion.
    \item Section~\ref{sec:population_size} will investigate the relationship
        between performance for differing population sizes. This highlights the
        importance of considering population dynamics over large populations.
    \item Section~\ref{sec:fitness} will calculate the relative fitness of all
        strategies.
\end{itemize}

@@

% TODO Move the case 2 graphics to here.

@@

In this section \(x_i\) will be investigated: the probability of 1 individual of
a given type successfully becoming fixated in a population of \(N - 1\) other
individuals. Figures~\ref{fig:fixation_heatmap_invade} shows these values for
the players along the vertical axis when matched against the players on the
horizontal axis. It can be seen that invasion is in general more challenging for
\(N=7\) and \(N=11\) in comparison to \(N=2\).
%TODO Change this to N=14
This information is summarised in Figure~\ref{fig:fixation_boxplot_invade}
showing the median fixation as well as the neutral fixation for each given
scenario.

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_2_invade.pdf}
        \caption{\(N=2\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_7_invade.pdf}
        \caption{\(N=7\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_11_invade.pdf}
        \caption{\(N=11\)}

@@

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_2_invade.pdf}
        \caption{\(N=2\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_7_invade.pdf}
        \caption{\(N=7\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_11_invade.pdf}
        \caption{\(N=11\)}
    \end{subfigure}%

@@

For \(N\in\{2, 7, 11\}\) the top five strategies are given in
% TODO Change N=11 to N=14
Tables~\ref{tbl:top_five_invade}. It can be seen that for \(N=2\), as described
in~\cite{Press2012}, zero determinant strategies perform well. There is a
single strategy with infinite memory in the top five but this is in fact a meta
strategy that plays with a team of memory one strategies picking out the top
performer at each stage. The remaining strategy ``Feld" is the corresponding
strategy submitted to the first tournament by Axelrod~\cite{Axelrod1980a}. All
these strategies are stochastic.

\begin{table}[!hbtp]
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{../tbl/summary_top_2_invade.tex}
        \caption{\(N=2\)}
    \end{subfigure}
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{../tbl/summary_top_7_invade.tex}
        \caption{\(N=7\)}
    \end{subfigure}
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{../tbl/summary_top_11_invade.tex}
        \caption{\(N=11\)}
    \end{subfigure}
    %TODO Change N=11 to N=14
    \caption{Properties of top five invaders}
    \label{tbl:top_five_invade}
\end{table}

@@

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_2_invade.pdf}
        \caption{\(N=2\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_7_resist.pdf}
        \caption{\(N=7\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_11_resist.pdf}
        \caption{\(N=11\)}

@@

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_2_invade.pdf}
        \caption{\(N=2\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_7_resist.pdf}
        \caption{\(N=7\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_11_resist.pdf}
        \caption{\(N=11\)}
    \end{subfigure}%

@@

\begin{table}[!hbtp]
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{../tbl/summary_top_7_resist.tex}
        \caption{\(N=7\)}
    \end{subfigure}
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{../tbl/summary_top_11_resist.tex}
        \caption{\(N=11\)}
    \end{subfigure}
    %TODO Change N=11 to N=14
    \caption{Properties of top five strategies resistors}
    \label{tbl:top_five_invade}
\end{table}

@@

@@

% TODO Redo everything with Meta strategies? This was a comment by MH. I suggest
% we leave this for this paper.

>>>>

The analytical models of a Moran process are based on the relative fitness
between two strategies and take this to be a fixed value \(r\) \cite{Nowak}.
This is a valid model for simple strategies of the Prisoner's Dilemma such as to
\textit{always cooperate} or \textit{always defect}. This manuscript provides a
detailed numerical analysis of \textbf{164} complex and adaptive strategies for
the IPD\@. In this case the relative fitness of a strategy is dependent on the
population distribution.

@@

The contribution of this work is a detailed and extensive analysis of absorption
probabilities for 164 strategies. These strategies and the numerical simulations
are from~\cite{axelrodproject} which is an open source research library written
for the study of the IPD\@. The strategies and simulation frameworks are
automatically tested in accordance to best research software practice. The large
number of strategies are available thanks to the open source nature of the
project with over 40 contributions made by different programmers. Thus by
considering Moran processes with population size greater than 2 we are taking in
to account the effect of complex population dynamics. By considering
sophisticated strategies we are taking in to effect the reputation of a strategy
during each interaction.

@@

To carry out this large numerical experiment 164 strategies are used from
\cite{axelrodproject}. These include 161 default strategies in the library at
the time (excluding strategies classified as having a long run time and those
that make use of the length of the game) as well as
the following 3 finite state machine machine strategies \cite{Ashlock2006}:

@@

Figure~\ref{fig:number_of_stochastic_match_outcomes} shows the distribution of
the number of outcomes between all strategy pairs.
Tables~\ref{tbl:number_of_stochastic_match_outcomes} shows that 95\% of the
stochastic matches have less than 788 unique outcomes whilst the maximum number
is 971. This ensures that using a set of cached results from 1000 precomputed
matches is sufficient for the analysis taking place here.

@@

Figure~\ref{fig:comparison_stochastic} shows the fixation probabilities for
stochastic strategies. These are no longer a good match which highlights the
weakness of the analytical formulae that relies on the average payoffs. A
detailed analysis of the 164 strategies considered, using direct Moran processes
will be shown in the next Section.

@@

\begin{itemize}
    \item Section~\ref{sec:two_individuals} will consider the specific case of
        \(N=2\).
    \item Section~\ref{sec:strong_invaders} will investigate the effect of
        population size on the ability of a strategy to invade another
        population. This will highlight how complex strategies with long
        memories outperform simpler strategies.
    \item Section~\ref{sec:strong_resistors} will similarly investigate the
        ability to defend against an invasion.
    \item Section~\ref{sec:population_size} will investigate the relationship
        between performance for differing population sizes. This highlights the
        importance of considering population dynamics over large populations.
    \item Section~\ref{sec:relative_fitness} will calculate the relative fitness of all
        strategies.
\end{itemize}

@@

The main fixation probabilities of interest are \(x_1\) and \(x_{N-1}\), these
reflect a strategy's ability to invade or resist invasion.
% TODO Perhaps mention that a lot of the research in to training fixation of
% strategies assumes N=2? Is this true?
For \(N=2\) these two cases coincide. Figure~\ref{fig:fixation_heatmap_2} shows
all pairwise fixation probabilities for strategies on the vertical column when
being matched against probabilities on the horizontal column. This is summarised
in Figure~\ref{fig:boxplot_2} and Table~\ref{tbl:summary_top_2} It can be seen
that, as described in in~\cite{Press2012}, zero determinant strategies perform
well. The strategy with infinite memory \texttt{Collective} is a strategy with a
handshake which implies that it will perform well against itself.. There is also
one of the trained finite state machines in the top five.  The remaining
strategy ``Feld" is the corresponding strategy submitted to the first tournament
by Axelrod~\cite{Axelrod1980a}. All these strategies are stochastic.

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=.5\textwidth]{../img/fixation_heatmap_2_invade.pdf}
    \caption{The pairwise fixation probabilities for \(N=2\)}
    \label{fig:fixation_heatmap_2}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[height=.5\textheight]{../img/boxplot_2_invade.pdf}
    \caption{The median fixation probabilities for \(N=2\)}
    \label{fig:boxplot_2}
\end{figure}

\begin{table}[!hbtp]
    \centering
    \input{../tbl/summary_top_2_invade.tex}
    \caption{Summary of top five strategies for \(N=2\)}
    \label{tbl:summary_top_2}
\end{table}

As will be demonstrated in Section~\ref{sec:population_size} \(N=2\)
is a particular case. In the next sections we will pay close attention to
strategies who are strong invaders/resistors and shown diagrammatically in
Figure~\ref{fig:invasion_resistance}.

\begin{figure}[!hbtp]
    \centering
    \input{../img/invasion_resistance.tex}
    \caption{A single individual will successfully invade the population with
    probability \(x_1\). The group of Individuals will successfully resist with
    probability \(x_{N-1}\)}
    \label{fig:invasion_resistance}
\end{figure}

@@

In this section \(x_i\) will be investigated: the probability of 1 individual of
a given type successfully becoming fixated in a population of \(N - 1\) other
individuals. Figures~\ref{fig:fixation_heatmap_invade} shows these values for
the players along the vertical axis when matched against the players on the
horizontal axis. It can be seen that invasion is in general more challenging for
\(N=7\) and \(N=11\) in comparison to \(N=3\).
%TODO Change this to N=14
This information is summarised in Figure~\ref{fig:fixation_boxplot_invade}
showing the median fixation as well as the neutral fixation for each given
scenario.

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_3_invade.pdf}
        \caption{\(N=3\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_7_invade.pdf}
        \caption{\(N=7\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_11_invade.pdf}
        \caption{\(N=11\)}

@@

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_3_invade.pdf}
        \caption{\(N=3\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_7_invade.pdf}
        \caption{\(N=7\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_11_invade.pdf}
        \caption{\(N=11\)}
    \end{subfigure}%

@@

For \(N\in\{3, 7, 11\}\) the top five strategies are given in
% TODO Change N=11 to N=14
Tables~\ref{tbl:top_five_invade}.

\begin{table}[!hbtp]
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{../tbl/summary_top_3_invade.tex}
        \caption{\(N=3\)}
    \end{subfigure}
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{../tbl/summary_top_7_invade.tex}
        \caption{\(N=7\)}
    \end{subfigure}
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{../tbl/summary_top_11_invade.tex}
        \caption{\(N=11\)}
    \end{subfigure}
    %TODO Change N=11 to N=14
    \caption{Properties of top five invaders}
    \label{tbl:top_five_invade}
\end{table}

@@

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_3_resist.pdf}
        \caption{\(N=3\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_7_resist.pdf}
        \caption{\(N=7\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_11_resist.pdf}
        \caption{\(N=11\)}

@@

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_3_resist.pdf}
        \caption{\(N=2\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_7_resist.pdf}
        \caption{\(N=7\)}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/boxplot_11_resist.pdf}
        \caption{\(N=11\)}
    \end{subfigure}%

@@

\begin{table}[!hbtp]
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{../tbl/summary_top_3_resist.tex}
        \caption{\(N=3\)}
    \end{subfigure}
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{../tbl/summary_top_7_resist.tex}
        \caption{\(N=7\)}
    \end{subfigure}
    \begin{subfigure}[t]{\textwidth}
        \centering
        \input{../tbl/summary_top_11_resist.tex}
        \caption{\(N=11\)}
    \end{subfigure}
    %TODO Change N=11 to N=14
    \caption{Properties of top five strategies resistors}
    \label{tbl:top_five_invade}
\end{table}

@@

\subsection{Relative fitness}\label{sec:relative_fitness}

Under the assumption of a constant relative fitness \(r\) between two
strategies~\cite{Nowak} the formula for \(x_i\) (for given \(N, r\) is:

\begin{equation}\label{equ:fixation_probability_with_constant_relative_fitness}
    x_i = x_i(r) = \frac{1-\frac{1}{r^{i}}}{1-\frac{1}{r^{N}}}
\end{equation}

Figure~\ref{fig:fixation_v_fitness_illustration} shows this function for
\(N=10\) and \(i\in\{1, 5, 10\}\).

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=.6\textwidth]{../img/fixation_v_fitness_illustration.pdf}
    \caption{\(x_i(r)\)}
    \label{fig:fixation_v_fitness_illustration}
\end{figure}

The first and second derivative of
(\ref{equ:fixation_probability_with_constant_relative_fitness}) is given by equations
(\ref{equ:fixation_probability_with_constant_relative_fitness_prime}) and
(\ref{equ:fixation_probability_with_constant_relative_fitness_prime2}).

\begin{equation}\label{equ:fixation_probability_with_constant_relative_fitness_prime}
    \frac{dx_i}{dr} = \input{../tbl/fixation_probability_with_constant_relative_fitness_prime.tex}
\end{equation}

\begin{equation}\label{equ:fixation_probability_with_constant_relative_fitness_prime2}
    \frac{d^2x_i}{dr^2} = \input{../tbl/fixation_probability_with_constant_relative_fitness_prime2.tex}
\end{equation}

Using these, Halley's method \cite{Alefeld2012} can be used to efficiently
numerically invert \(x_i(r)\) to obtain a theoretic relative fitness \(r\) that
gives the calculated \(x_i(r)\) between two strategies for a given \(N, i\).
% TODO Say more things: I still think this is a bit cylic. The formula we are
% using assumes a constant relative fitness which we know does not exist.

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/Alternator_v_Cooperator_fitness.pdf}
        \caption{Alternator and Cooperator}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/Alternator_v_Defector_fitness.pdf}
        \caption{Alternator and Defector}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/Alternator_v_Tit_For_Tat_fitness.pdf}
        \caption{Alternator and Tit For Tat}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/Cooperator_v_Tit_For_Tat_fitness.pdf}
        \caption{Cooperator and Tit For Tat}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/Defector_v_Cooperator_fitness.pdf}
        \caption{Defector and Cooperator}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/Defector_v_Tit_For_Tat_fitness.pdf}
        \caption{Defector and Tit For Tat}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/Win-Stay_Lose-Shift_v_Tit_For_Tat_fitness.pdf}
        \caption{Win Stay Lose Shift and Tit For Tat}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/Alternator_v_Win-Stay_Lose-Shift_fitness.pdf}
        \caption{Alternator and Win Stay Lose Shift}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/Defector_v_Win-Stay_Lose-Shift_fitness.pdf}
        \caption{Defector and Win Stay Lose Shift}
    \end{subfigure}%
    \caption{Estimated relative fitness
             for \textbf{deterministic} strategies}
    \label{fig:comparison_deterministic}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/Random_v_Cooperator_fitness.pdf}
        \caption{Random and Cooperator}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/Random_v_Defector_fitness.pdf}
        \caption{Random and Defector}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/Random_v_Tit_For_Tat_fitness.pdf}
        \caption{Random and Tit For Tat}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/ALLCorALLD_v_Cooperator_fitness.pdf}
        \caption{All C or all D and Cooperator}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/ALLCorALLD_v_Defector_fitness.pdf}
        \caption{All C or all D and Defector}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/Calculator_v_Random_fitness.pdf}
        \caption{Calculator and Random}
    \end{subfigure}%

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/Calculator_v_ALLCorALLD_fitness.pdf}
        \caption{Calculator and All C or all D}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/Calculator_v_Arrogant_QLearner_fitness.pdf}
        \caption{Calculator and Arrogant Q learner}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/ALLCorALLD_v_Tit_For_Tat_fitness.pdf}
        \caption{All C or all D and Tit For Tat}
    \end{subfigure}%
    \caption{Estimated relative fitness
             for \textbf{stochastic} strategies}
    \label{fig:comparison_stochastic}
\end{figure}

@@
